Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-15 ms.qmd
Adding in all habitat types. Prepred for monday

>>>>

######################################################################
# Model predcitions for terrestrial, marine and freshwater ectotherms
######################################################################
# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.

## Terrestrial Ectotherms
  terrest_data <- sub_data  %>% filter(habitat == "t")
    new_data_t <- data.frame(
      spp = terrest_data$spp,
      trait = terrest_data$trait,
      habitat = terrest_data$habitat,
      c_accl_time = 0,
      V = 0,
      lat = terrest_data$lat.y,
      long = terrest_data$long.x
    )

terre_pred <- predict(model5_bayes, newdata = new_data_t, summary = FALSE)

## Marine ectotherms  
  marine_data <- sub_data  %>% filter(habitat == "m")
    new_data_m <- data.frame(
      spp = marine_data$spp,
      trait = marine_data$trait,
      habitat = marine_data$habitat,
      c_accl_time = 0,
      V = 0,
      lat = marine_data$lat.y,
      long = marine_data$long.x
    )

marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = FALSE)

## Freshwater ectotherms
  fresh_data <- sub_data  %>% filter(habitat == "f")
    new_data_f <- data.frame(
      spp = fresh_data$spp,
      trait = fresh_data$trait,
      habitat = fresh_data$habitat,
      c_accl_time = 0,
      V = 0,
      lat = fresh_data$lat.y,
      long = fresh_data$long.x
    )

fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = FALSE)
